Clearance Project - 3 - TKstats

### 2025-03-20 data-raw/ClearanceProject-3-TKstats.Rmd

Next what we want to do is get httk predictions for nonrestrictive & 
restrictive chemicals, but going from

```{r}

>>>>

This next analysis looks at bootstrapping to look at specific variation in downstream
parameters (like Css and halflife) which depend on _kelim_ which cannot be estimated
at times. However, it is noted that even this method does not provide much more information.
